\speculake: Hiding Malware in Speculative Execution

### 2018-08-01 paper/related-work.tex
rewording

Previous examples of weird machines include traditional vulnerabilities such as
buffer overflows, format string exploits and return-to-libc attacks without
function calls~\cite{buffer_overflow, format_string_exploit,
shacham2007geometry}.

Unexpected functionality such as instruction-less
computing~\cite{bangert2013page} enables the demonstration of a Turing complete
weird machine by taking advantage of memory translation tables, page-faults, and
hardware exception handling to effectively compute arithmetic and logical
operations without the processor executing any instructions.

@@

Whereas previous weird machines have demonstrated the capability to execute
potentially malicious code in an unexpected manner, \speculake is a new type of
``weird machine'' that takes advantage of speculative execution and uses a
non-complicit trigger program to execute otherwise dead code.

>>>>

Previous examples of ``weird machines'' include traditional vulnerabilities such
as buffer overflows, format string exploits and return-to-libc attacks without
function calls~\cite{buffer_overflow, format_string_exploit,
shacham2007geometry}.

Unexpected functionality such as instruction-less computing enables the
demonstration of a Turing complete weird machine by taking advantage of memory
translation tables, page-faults, and hardware exception handling to effectively
compute arithmetic and logical operations without the processor executing any
instructions~\cite{bangert2013page}.

@@

Previous ``weird machines'' have demonstrated the capability to execute
potentially malicious code in an unexpected manner, and \speculake is a new type
of ``weird machine'' that takes advantage of speculative execution and uses a
non-complicit trigger program to execute otherwise dead code.
